\input{hwheader}
\author{Programming for Scientists}
\title{Homework 4}
\date{Feb 17}
\begin{document}
\maketitle

\chapter{Questions}

\question % 1
Alice and Bob are pair-programming again. This time, Alice writes the following code:

\begin{python}
print 'Error: file format unrecognised.'
\end{python}

Bob suggests that, since this is an error, it should be 

\begin{python}
import sys
...

print >>sys.stderr, 'Error: file format unrecognised.'
\end{python}

Alice argues ``Both go to the screen when I run the program, so printing errors to \lstinline{sys.stderr} is just being pedantic.'' Bob says ``Well, if you run it directly, both stdout and stderr go to the screen, but you can redirect stdout or pipe it to some other program and then it makes a big difference.''

What is Bob talking about? (You can simply give an example of where things work differently if you use Bob or Alice's version.)

\question % 2
Recall the printargs.py script:

\begin{python}
import sys
print len(sys.argv)
print sys.argv
\end{python}

What gets printed when you run the following (the dollar sign is the prompt):

\begin{verbatim}
$python printargs.py
$python printargs.py one two three
$python printargs.py *.py
$python printargs.py *py
\end{verbatim}

\chapter{Programming Assignment}
Create a subversion repository in one computer and check-out in another. (You are going to have to read up on this or look through the show-me-do video: check the website for links).

\begin{enumerate}
\item Create a Subversion repository.
\item Create a checkout in another computer.
\item Add a file \texttt{hello.py} which prints 'Hello World'
\item Change the file to print more things.
\item Commit that change.
\item Make some new change.
\item Run \texttt{svn diff} and email me the results.
\end{enumerate}

\end{document}
