\input{hwheader}
\author{Programming for Scientists}
\title{Homework 6}
\date{Mar 3}
\begin{document}
\maketitle

\chapter{Questions}

\question % 1
What is under-flow (when talking about numerical precision)?

\question % 2
What is the smallest value (i.e., smallest absolute value) that a 32~bit \textsc{ieee-754} float can represent? (Hint: Wikipedia has the answer to this question).

\question % 3
You will sometimes see the following programming idiom:

\begin{python}
import numpy as np
mystery = np.uint32(-1)
\end{python}

What is the value of mystery? Why would we be interested in this particular value? (Hint: think of its bit representation).

\question % 4
With numpy, we saw that we could easily create an array of 32~bit numbers:

\begin{python}
import numpy as np
A = np.array([1,2,3,4,5],np.int32)
\end{python}

However, it is also possible to simply use a traditional Python list:

\begin{python}
A = [1,2,3,4,5]
\end{python}

This has the advantage of using Python numbers, which are of infinite precision, instead of being limited to 32~bits. Given this obvious disadvantage, why would anyone use the 32~bit array? (There is more than one reason, but you only need to give one).

\question % 5
Consider the following code

\begin{python}
import numpy as np
...
M = A.ptp(0)
\end{python}

If $A$ is of shape $(120,1000)$, what is the resulting shape of $M$? What does the ptp function return?

\chapter{Programming Assignment}

Consider the following approximation to compute an integral:

\begin{equation}
\int_0^{1} f(x)dx \approx \sum_{i = 0}^{999} \frac{f(i/1000)}{1000}.
\end{equation}

\begin{enumerate}
\item Implement two versions of this for integrating $f(x) = x^2$. One should use ``pure Python'' (i.e., you should not require any \lstinline{import}s). Another should be based on \lstinline{numpy} (where you compute all the values $f(i/1000)$ in a single step).
\item Determine which version is faster. (Hint: You might need to run each version a many times to be able to get a meaningful answer.)
\end{enumerate}

\end{document}
