\input{slheader}
\title{Scipy, OpenOpt \& Projects}
\begin{document}
\frame{\maketitle}

\begin{frame}[fragile]
\frametitle{Scipy}

\begin{block}{Scipy}
\begin{itemize}
\item A collection of libraries for scientific computing.
\item Current version: 0.7 (February 2009).
\end{itemize}
\end{block}

\end{frame}

\begin{frame}[fragile]
\frametitle{Scipy: main modules}

\begin{itemize}
\item linalg: linear algebra
\item stats: probability and statistics
\item ndimage: n-dimensional image processing.
\item \ldots
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{Matplotlib}
Matplotlib is a \alert{plotting library} for Python.

\begin{python}
import pylab
import numpy as np
X = np.linspace(-4,+4,1000)
pylab.plot(X,np.exp(-X**2))
pylab.xlabel(r'$x$')
pylab.ylabel(r'$\exp(-x^{2})$)
pylab.savefig('gaussian.pdf')
\end{python}

\centering
\href{http://matplotlib.sf.net/}{http://matplotlib.sf.net/}

\end{frame}

\begin{frame}[fragile]
\frametitle{Projects}

There is a small final project.

\begin{enumerate}
\item Self-proposed.
\item Class project.
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Class Project}

Let's see the motivation video (credit: Rebecca Webb and Brooke McCartney)
\end{frame}

\begin{frame}[fragile]
\frametitle{Simulation Project}

\begin{enumerate}
\item Simulate a video
\item Track on the video
\item Compare the results
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Project}
\begin{enumerate}
\item Object position generator
\item Image generator
\item Object detection
\item Object tracking
\item Results visualisation
\item Statistics gathering
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Project Logistics}

\begin{block}{Design}
I will use the project as a design ``case study'' for a medium sized project.
\end{block}

\begin{block}{Infrastructure}
\begin{itemize}
\item Open source (i.e., we will post the code online for others to use).
\item Common Subversion repository.
\item Email discussions.
\item Nosetest tests.
\end{itemize}
\end{block}

\end{frame}

\end{document}
