\input{slheader}
\title{Distribution of Software}
\begin{document}
\frame{\maketitle}

\begin{frame}[fragile]
\frametitle{Open Source}
What is open-source?
\end{frame}

\begin{frame}[fragile]
\frametitle{Intellectual Property}
Wikipedia-level introduction to intellectual property:
\begin{enumerate}
\item copyright
\item patent \note{software is patentable in the US, but not in other jurisdictions [EU]}
\item trademark
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Licenses}
A license is a \alert{loosening} of the default ``All Rights Reserved'' framework.
\note{
    Note that the code is owned either by he who writes it or by their lab/university/\ldots
}
\end{frame}

\begin{frame}[fragile]
\frametitle{Licenses}
\begin{enumerate}
\item Public-domain
\item BSD or MIT licenses
\item GPL (copy-left)
\item Author License
\item \ldots (10~million others)
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Public Domain}

I can do whatever I want.

\bigskip
You can release the code into the public domain.
\end{frame}

\begin{frame}[fragile]
\frametitle{MIT License}

Permission is hereby granted, free of charge, to any person
obtaining a copy of this software and associated documentation
files (the "Software"), to deal in the Software without
restriction, including without limitation the rights to use,
copy, modify, merge, publish, distribute, sublicense, and/or sell
copies of the Software, and to permit persons to whom the
Software is furnished to do so, subject to the following
conditions:

The above copyright notice and this permission notice shall be
included in all copies or substantial portions of the Software.
\end{frame}

\begin{frame}[fragile]
\frametitle{BSD 3-Clause license}

Redistribution and use in source and binary forms, with or without
modification, are permitted provided that the following conditions are met:
\begin{enumerate}
\item Redistributions of source code must retain the above copyright notice, this list of conditions and the following disclaimer.
\item Redistributions in binary form must reproduce the above copyright notice, this list of conditions and the following disclaimer in the documentation and/or other materials provided with the distribution.
\item Neither the name of the <organization> nor the names of its contributors may be used to endorse or promote products derived from this software without specific prior written permission.
\end{enumerate}

\end{frame}

\begin{frame}[fragile]
\frametitle{Non-Code Open Source}

\begin{itemize}
\item Creative Commons.
\item GFDL
\item \ldots
\end{itemize}
\note{
    GFDL is the GNU Free Documentation License, on which Wikipedia is based.
}
\end{frame}

\begin{frame}[fragile]
\frametitle{Creative Commons}

\begin{block}{Restrictions}
\begin{itemize}
\item \alert{Attribution} [By] you need to state the source
\item \alert{Non-Commercial} [NC] you cannot use it for commercial purposes
\item \alert{Non-Derivative} [ND] you may not modify the work
\item \alert{Share-Alike} [SA] you must license your derivative works similarly 
\end{itemize}
\note{
    These are all a bit 'undefined' and mostly un-tested by case law.

    What counts as non-commercial, for example?
}
\end{block}

Mix \& match to get a license, e.g., By-NC-SA.\note{
    This is the license of the class.
}
\end{frame}

\end{document}
