\input{slheader}
\title{SQL: Database Access}
\begin{document}
\frame{\maketitle}

\begin{frame}[fragile]
\frametitle{Using Databases}

Problem
\begin{itemize}
\item Many different ``experiments''.
\item Each experiment has input parameters and output measurements.
\end{itemize}

\end{frame}

\begin{frame}[fragile]
\frametitle{Database Design}

Experiments with input parameters and output values.

\pause
Tables
\begin{enumerate}
\item Experiments
\item Experiment parameters
\item Experiment results
\end{enumerate}

\end{frame}

\begin{frame}[fragile]
\frametitle{SQL For Table Creation}

\begin{verbatim}
CREATE TABLE experiments (
    eid INT PRIMARY KEY,
    name VARCHAR(255),
    date DATE NOT NULL
    );
CREATE TABLE parameters (
    pid INT PRIMARY KEY,
    name VARCHAR(255) NOT NULL
    );
CREATE TABLE experiment_parameters (
    eid INT NOT NULL,
    pid INT NOT NULL,
    paramvalue VARCHAR(255)
    );
CREATE TABLE experiment_results (
    eid INT NOT NULL,
    measure VARCHAR(255),
    value VARCHAR(255)
    );
\end{verbatim}
\end{frame}

\begin{frame}[fragile]
\frametitle{Example Query}
\begin{verbatim}
SELECT name, date
FROM experiments, parameters, experiment_parameters
WHERE experiments.eid = experiment_parameters.eid AND
    experiment_parameters.pid = paramenters.pid AND
    parameters.name = 'Generation/model' AND
    experiment_parameters.paramvalue = 'brownian';
\end{verbatim}
\end{frame}

\begin{frame}[fragile]
\frametitle{A Traditional Database Management System}

\begin{enumerate}
\item Install it.
\item Set it up to run as daemon.
\item Create database(s).
\item Create user(s).
\item Create tables.
\item Use it.
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{SQLite: Database in a File}

SQLite implements SQL-like databases in a single file.
\end{frame}

\begin{frame}[fragile]
\frametitle{Using SQLite}

\begin{python}
import sqlite3
from os.path import exists
filename = 'experiment.db'
create = not exists(filename)
connection = sqlite3.connect(filename)
cursor = connection.cursor()
if create:
    cursor.execute('''
        CREATE TABLE ...''')
\end{python}
\end{frame}

\begin{frame}[fragile]
\frametitle{Using SQLite (II)}

cursor.execute('''
    SELECT eid,name,date
    FROM experiments
    WHERE date > DATE('2008-12-01')
    ''')

for eid,name,date in cursor.fetchall():
    print eid, name, date
\end{frame}

\begin{frame}[fragile]
\frametitle{PyTables}
A different type of database,\\
based on \alert{HDF5}.
\end{frame}


\end{document}
