\input{slheader}
\title{Introduction to Python Programming}
\begin{document}

\frame{\maketitle}

\note{
    Goals for this session:

    - Be able to run a program.
    - Be able to run interactively.

    - Rough understanding of name/object concept.
    - Understand control flow.
}

\begin{frame}[fragile]
\frametitle{What is a Computer?}

\begin{enumerate}
\item Memory
\item Processor
\item Magic
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Python Model}

\begin{enumerate}
\item Objects
\item Operations on objects
\item Magic
\end{enumerate}
\end{frame}

\begin{frame}[fragile]
\frametitle{Computer Program}

\begin{block}{helloword.py}
\begin{python}
print 'Hello World'
\end{python}
\end{block}
\end{frame}

\begin{frame}[fragile]
\frametitle{Running a Program}
\begin{enumerate}
\item Shell
\item IDE
\end{enumerate}
\end{frame}

\begin{frame}[fragile]

\bigskip
\bigskip
\bigskip
Let me show you a demonstration\ldots

\note{
\begin{enumerate}
\item Demo shell with vim
\item Demo one IDE
\end{enumerate}
}


\end{frame}

\begin{frame}[fragile]
\frametitle{More Complex Example}

What is 25 + 20\%?

\pause
\begin{python}
print 25 * 1.2
\end{python}
\note{Demo the python shell.

This is basically a glorified calcular}
\end{frame}

\begin{frame}[fragile]
\frametitle{Tip Calculator}

\begin{block}{Calculator}
\begin{enumerate}
\item Input: initial amount and the tip percentage.
\item Ouput: final amount.
\end{enumerate}
\end{block}
\end{frame}

\begin{frame}[fragile]
\frametitle{Blackboard demonstration}

\note{Use the blackboard to introduce the idea of objects, values and names.}
\end{frame}

\begin{frame}[fragile]
\frametitle{Flow of Control: Conditionals}

\begin{block}{Tip Calculator (II)}
\begin{enumerate}
\item Input: initial amount and service quality.
\item Output: final amount.
\end{enumerate}
\end{block}

\note{
\begin{python}
initial = ..

quality = ..

if quality == 'great':
    percentage = 20
else:
    percentage = 15

print initial * (1+percentage/100.0)

\# discuss 
\end{python}
}

\end{frame}

\begin{frame}[fragile]
\frametitle{Conditionals}

\begin{python}

if <condition>:
    <statement 1>
    <statement 2>
else:
    <statement 3>

\end{python}
\end{frame}

\begin{frame}[fragile]
\frametitle{Lists}

\begin{python}

students = ['Luis','Mark','Rita']

print students[0]
print students[1]
print students[2]
\end{python}

\end{frame}

\begin{frame}[fragile]
\frametitle{Loops}

\begin{python}
students = ['Luis','Mark','Rita',...]

for st in students:
    print st
\end{python}
\end{frame}

\begin{frame}[fragile]
\frametitle{Loops (II)}

\begin{python}

students = ['Luis',...]

looking_for = 'Anna'

i = 0
while students[i] != looking_for:
    i += 1

if students[i] == looking_for:
    print 'Found her'
else:
    print "Sorry, she's not registered!"
\end{python}

\end{frame}

\end{document}
